Lobbying and Legislative Uncertainty

### 2016-05-10 presentation.tex
fix footline; add B's full program

\usepackage{cite}
\usepackage{times, verbatim,xcolor,bm}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{amsbsy,amssymb, amsmath, amsthm}
\usepackage{booktabs}
%David miller's fonts
	\usepackage[T1]{fontenc}
	\usepackage[boldsans]{ccfonts}
	%\usepackage[boldsans]{concmath}
	\usepackage[euler-hat-accent]{eulervm}

@@

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
\author[Buzard and Saiegh \hspace{3in} \url{kbuzard@syr.edu}]{Kristy Buzard\inst{1} \and Sebastian Saiegh\inst{2}}
\institute{\inst{1}Syracuse University and The Wallis Institute \and 
\inst{2}UC San Diego}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

>>>>

\usepackage{cite}
\usepackage{times,xcolor,bm}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{amsbsy,amssymb, amsmath, amsthm}
\usepackage{booktabs}
%David miller's fonts
	\usepackage[T1]{fontenc}
	\usepackage[boldsans]{ccfonts}
	%\usepackage[boldsans]{concmath}
	\usepackage[euler-hat-accent]{eulervm}

@@

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
\author[Buzard and Saiegh]{Kristy Buzard\inst{1} \and Sebastian Saiegh\inst{2}}
\institute{\inst{1}Syracuse University and The Wallis Institute \\ \url{kbuzard@syr.edu} \and 
\inst{2}UC San Diego}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\begin{frame}{Vote Buyer B's Full Program}
\pause
\begin{equation}
    \left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1 - \lambda_X}{W_B}
		\label{eq:focB}
\end{equation}
\begin{equation}
    \left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1 - \lambda_Y}{W_B}
\end{equation}
\begin{equation}
    \left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2} = \frac{1 - \lambda_Z}{W_B}
\end{equation}
\[
  b\left(0\right) \geq0 \hskip.2in b\left(-.5\right) \geq0 \hskip.2in b\left(.5\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-.5\right) = 0 \hskip.2in \lambda_Z \cdot b\left(.5\right) = 0 
\]
